Progress Report for CSS 586: \\ Modeling Latent Patterns in Music

### 2021-04-19 papers/progress/alex/progress-alex.tex
save progress report paper work

Depending on the task, machine learning models of music may be trained on the
audio signal itself, either in a time domain or a frequency domain
representation, or they may be trained on a digital symbolic representation of
music, the most common of which is MIDI (Musical Instrument Digital Interface)
notation. MIDI is an encoding of music as streams of bytes in one or more tracks
or channels, each representing a sequence of 128 possible pitch values, along
with timing, pressure and instrument values. A music transcription model may
convert an audio signal into MIDI (which can then be transcribed into sheet
music), while a synthesizer model can convert MIDI representations into audio
signals.

@@

>>>>

Depending on the task, machine learning models of music may be trained on the
audio signal itself, either in a time domain or a frequency domain
representation, or they may be trained on a digital symbolic representation of
music, the most common of which is MIDI (Musical Instrument Digital Interface)
notation. MIDI is an encoding of music as streams of bytes in one or more tracks
or channels, each representing a sequence of 128 possible pitch values, along
with timing, pressure and instrument values. A music transcription model may
convert an audio signal into MIDI, which can easily be converted into other
symbolic representations such as sheet music, while a synthesizer model can
convert MIDI representations into audio signals.

@@

Other research has focused on modeling raw audio waveforms directly. WaveNet is
a causal convolutional neural network for generating raw audio waveforms,
developed by Google DeepMind, which achieves state of the art performance in
generating natural sounding speech from text, but is also capable of generating
short, realistic snippets of audio music \cite{oord_wavenet_2016}. Another model
named SampleRNN generates raw audio waveforms using a three-tier hierarchy of
gated recurrent units (GRU) to model recurrent structure at multiple temporal
resolutions \cite{mehri_samplernn_2017}.

A paper from Boston University describes an effort to combine the symbolic and
waveform approaches to music modeling \cite{manzelli_conditioning_2018}.
